Adaption of the Chumbley Score to matching of bullet striation marks

### 2017-10-11 doc/paper.Rmd
small stuff

\hh{table with an overview of the different parameter settings}
```{r echo=FALSE}
param_setting<- all %>% select(wo, wv) %>% group_by(wo, wv) %>% tally() %>% select(wo,wv)
#param_setting
param_setting %>% tally() 
```

@@

```{r type2, fig.width=8, fig.height=5, out.width='\\textwidth', fig.cap="Type II error rates observed across a range of window sizes for optimization $wo$. For a window size of $wo = 120$ we see a drop in type II error rate across all type I rates considered. Smaller validation sizes $wv$ are typically associated with a smaller type II error."}
greens <- RColorBrewer::brewer.pal(name="Greens", n = 6)
errors %>% filter(wv %in% c(30,50)) %>%
  ggplot(aes(x = wo, y = beta, colour=factor(alpha))) + 
  geom_point(aes(shape=factor(wv))) +
#  facet_grid(.~wo, labeller="label_both") + 
  geom_smooth(aes(group=alpha), se=FALSE, method="loess") +
  theme_bw() +
  scale_colour_manual("Nominal type I error", values=greens[-(1:2)]) +
  scale_shape_discrete("Size of \nvalidation window") +
  xlab("Window size for optimization") +
  ylab("Type II error rate")
```

@@

```{r type1, fig.width=8, fig.height=5, out.width='\\textwidth', fig.cap="Comparison of observed and nominal type I error rates  across a range of window sizes for optimization $wo$. The horizontal line in each facet indicates the nominal type I error rate.  As the optimization window increase the observed type I error rate gets smaller. A smaller validation window tends to be associated with a higher type I error rate."}
errors %>% filter(wv %in% c(30,50)) %>%
  ggplot(aes(x = wo, y = actual, colour=factor(alpha))) + 
  geom_hline(aes(yintercept=alpha), colour="grey30") +
  geom_point(aes(shape=factor(wv))) +
  #  facet_grid(.~wo, labeller="label_both") + 
  geom_smooth(aes(group=alpha), se=FALSE, method="lm") +
  theme_bw() +
#  scale_y_log10(breaks=c(0.001,.005, 0.01, 0.05)) +
  scale_shape_discrete("Size of \nvalidation window") +
  ylab("Observed type I error rate") +
  xlab("Window size for optimization") +
  scale_colour_brewer("Nominal type I error alpha", palette="Set2") +
  facet_wrap(~alpha, labeller="label_both", scales="free") +
  theme(legend.position="bottom")

@@

```{r missings, fig.width=8, fig.height=5, fig.cap="Number of failed tests."}
ns <- all %>% group_by(wv, wo, match) %>% summarize(
  n_ss = mean(same_shift_n),
  n_ds = mean(diff_shift_n),
  zero_ss = sum(same_shift_n==0),
  zero_ds = sum(diff_shift_n==0),
  miss = sum(is.na(p_value)),
  missperc = miss/85491*100
)
ns %>% filter(wv %in% c(30, 50)) %>% 
  ggplot(aes(x = wo, y = missperc, shape=factor(wv), colour = factor(match))) + 
  geom_smooth(method="lm", size=.5, se=FALSE) +
  geom_point() + 
  theme_bw() +
  ylab("Percent of failed tests.") +
  xlab("Size of optimization window") +
  scale_colour_brewer("Match", palette="Set1") +
  scale_shape_discrete("Size of \nvalidation\nwindow")

```
Figure \ref{fig:missings} gives an overview of the number of failed tests, i.e. tests in which a particular parameter setting did not return a valid result. This happens, when the shift to align two signatures is so large, that the remaining overlap is too small to accommodate  windows for validation. The problem is therefore exacerbated by a larger validation window. 
Figure \ref{fig:missings} also shows that the number of failed tests is approximately linear in the size of the optimization window.

>>>>

\hh{table with an overview of the different parameter settings}
```{r, echo=FALSE, results='asis'}
param_setting<- all %>% select(wo, wv) %>% group_by(wo, wv) %>% tally() %>% select(wo,wv)
#t(param_setting)
#param_setting %>% tally()

knitr::kable(t(param_setting), digits=0, caption = "Overview of parameter settings used for optimization and validation windows for bullet land signatures.", booktabs=TRUE)
```

@@

```{r type2, fig.width=8, fig.height=5, out.width='\\textwidth', fig.cap="Type II error rates observed across a range of window sizes for optimization $wo$. For a window size of $wo = 120$ we see a drop in type II error rate across all type I rates considered. Smaller validation sizes $wv$ are typically associated with a smaller type II error."}
errors %>% filter(wv %in% c(30,50)) %>%
  ggplot(aes(x = wo, y = beta, colour=factor(alpha))) + 
  geom_point(aes(shape=factor(wv))) +
#  facet_grid(.~wo, labeller="label_both") + 
  geom_smooth(aes(group=alpha), se=FALSE, method="loess") +
  theme_bw() +
  scale_colour_brewer(expression("Nominal type I error"~alpha), palette="Set2") +
  scale_shape_discrete("Size of validation\nwindow, wv") +
  xlab(expression("Window size for optimization, "~wo)) +
  ylab("Type II error rate")

labels = expression(P[M1](tilde(z)>0),P[M0](tilde(z)>0))
```

@@

```{r type1, fig.width=8, fig.height=5, out.width='\\textwidth', fig.cap="Comparison of observed and nominal type I error rates  across a range of window sizes for optimization $wo$. The horizontal line in each facet indicates the nominal type I error rate.  As the optimization window increase the observed type I error rate gets smaller. A smaller validation window tends to be associated with a higher type I error rate."}
errors %>% filter(wv %in% c(30,50)) %>%
  ggplot(aes(x = wo, y = actual, colour=factor(alpha))) + 
  geom_hline(aes(yintercept=alpha), colour="grey30") +
  geom_point(aes(shape=factor(wv))) +
  #  facet_grid(.~wo, labeller="label_both") + 
  geom_smooth(aes(group=alpha), se=FALSE, method="lm") +
  theme_bw() +
#  scale_y_log10(breaks=c(0.001,.005, 0.01, 0.05)) +
  scale_shape_discrete("Size of validation window, wv") +
  ylab("Observed type I error rate") +
  xlab(expression("Window size for optimization, "~wo)) +
  scale_colour_brewer(expression("Nominal type I error "~alpha), palette="Set2") +
  facet_wrap(~alpha, labeller="label_both", scales="free") +
  theme(legend.position="bottom")

@@

```{r missings, fig.width=8, fig.height=5, fig.cap="Number of failed tests by the window optimization size, wo, and ground truth. Test results from different sources have a much higher chance to fail, raising the question, whether failed tests should be treated as rejections of the null hypothesis of same source."}
ns <- all %>% group_by(wv, wo, match) %>% summarize(
  n_ss = mean(same_shift_n),
  n_ds = mean(diff_shift_n),
  zero_ss = sum(same_shift_n==0),
  zero_ds = sum(diff_shift_n==0),
  miss = sum(is.na(p_value)),
  missperc = miss/85491*100
)
ns %>% filter(wv %in% c(30, 50)) %>% 
  ggplot(aes(x = wo, y = missperc, shape=factor(wv), colour = factor(match))) + 
  geom_smooth(method="lm", size=.5, se=FALSE) +
  geom_point() + 
  theme_bw() +
  ylab("Percent of failed tests.") +
  xlab("Size of optimization window, wo") +
  scale_colour_brewer("Match", palette="Set1") +
  scale_shape_discrete("Size of \nvalidation\nwindow, wv")
```
Figure \ref{fig:missings} gives an overview of the number of failed tests, i.e. tests in which a particular parameter setting did not return a valid result. This happens, when the shift to align two signatures is so large, that the remaining overlap is too small to accommodate  windows for validation. The problem is therefore exacerbated by a larger validation window. 
Figure \ref{fig:missings} also shows that the number of failed tests is approximately linear in the size of the optimization window.
